BlueTracer: \\ a Robust API Tracer for Evasive Malware

### 2018-07-14 Msc-Slides/main.tex
Slides Done

\begin{frame}
    \frametitle{Integration with BluePill}

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Al-Khaser}

@@

\begin{frame}
    \frametitle{Sample tracked evasive check}

@@

\subsection{Evasive malware samples}
\begin{frame}
    \frametitle{Evasive malware samples}

@@

\begin{frame}
    \frametitle{Conclusion and future developments}

>>>>

\begin{frame}
    \frametitle{Integration with BluePill}
	\textbf{BluePill} is a software toolkit which:
	\begin{itemize}
	\item Allows the simulation of a real production environment a specific malware
sample was intended for
	\item Conceals any virtualization artifacts and software setup which might set off
evasion
	\end{itemize}
	\medskip

	    \begin{figure}
    	\vspace{-0.3cm}
    	%\hspace*{1cm}
        \includegraphics[width=7.5cm]{image/BluePill.pdf}
    \end{figure}

@@

\subsection{Al-Khaser}
\begin{frame}
    \frametitle{Evaluation with Al-Khaser}
	\textbf{Al-Khaser} is an open-source application which performs common checks employed by malware families to determine if they are being
executed in an analysis environment
\\\medskip
Checks divided in categories:
\begin{itemize}
\item \textbf{Anti-Debugging}
\item \textbf{Timing-based}
\item \textbf{Human Interaction Detection}
\item \textbf{Anti-Virtualization}
\item \textbf{Anti-Analysis}
\end{itemize}
\bigskip
\begin{beamerboxesrounded}[shadow=true]{}
BlueTracer was undetected with respect to all the checks!
\end{beamerboxesrounded}

    \begin{textblock*}{3cm}(7.5cm,-4.cm)
   \includegraphics[width=2cm]{image/lights.png}% use the \includegraphics command here
	\end{textblock*}

@@

\begin{frame}[fragile]
    \frametitle{Example of tracked evasion check}

File system artifacts can be checked in order to uncover the presence of a virtualized environment
\vspace*{0.5cm}

    %\begin{figure}
    %	\vspace{-0.5cm}
    	%\hspace*{1cm}
    %    \includegraphics[width=11cm]{image/SampleCall}
    %\end{figure}

	\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=none, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    %keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\linespread{1.3}\footnotesize\ttfamily,
    basewidth = {.48em},
   escapeinside={<@}{@>}
}
\begin{lstlisting}
~~3160~~ 24980 KERNELBASE.dll!GetFileAttributesW
24980 	arg 0: <@\alert{C:Windows\textbackslash system32\textbackslash drivers\textbackslash VBoxMouse.sys}@>
 (name=lpFileName, type=wchar_t*, size=0x2)
24980    executed KERNELBASE.dll!GetFileAttributesW =>
24980 	retval: 0xffffffff (name=Return value, type=DWORD, size=0x4)
\end{lstlisting}
\lstset{
    language=C++,
    frame=tb, % draw a frame at the top and bottom of the code block
    tabsize=4, % tab space width
    showstringspaces=false, % don't mark spaces in strings
    numbers=left, % display line numbers on the left
    commentstyle=\color{ao}, % comment color
    keywordstyle=\color{blue}, % keyword color
    stringstyle=\color{red}, % string color
    basicstyle=\footnotesize\ttfamily,
    basewidth = {.48em}
}

@@

\subsection{Evasive malware samples}
\begin{frame}
    \frametitle{Evaluation with evasive malware samples}

	Five highly evasive samples collected by Joe Security:

    \begin{table}[h]
\vspace*{0.1cm}
\begin{center}
\resizebox{9.2cm}{!}{
 \begin{tabular}{||c c c||}
 \hline
 \textbf{ID} & \textbf{MD5} & \textbf{Name} \\ 
 \hline\hline
 1 & 0af4ef5069f47a371a0caf22ae2006a6 & \textit{trojan/banker} \\ 
 \hline
 2 & 9437eabf2fe5d32101e3fbf9f6027880 & \textit{dropper} \\
 \hline
 3 & cbdda646a20d95f078393506ecdc0796 & \textit{trojan}\\
 \hline
 4 & cfdd16225e67471f5ef54cab9b3a5558 & Olympic\\
 \hline
 5 & ef694b89ad7addb9a16bb6f26f1efaf7 & CCleaner\\ 
 \hline
\end{tabular}
}
\end{center}
\end{table}
\medskip
\begin{beamerboxesrounded}[shadow=true]{}
The
logs collected by BlueTracer reveal behaviors consistent with the analysis reports
authored by Joe Security
\end{beamerboxesrounded}

@@

\begin{frame}
    \frametitle{Conclusions}

	\textbf{\textcolor{sapienza}{Contribution:}} \\
	\smallskip	
	\tab Design and implementation of \textbf{BlueTracer},
a robust library and system call tracer for Windows programs specialized in evasive
malware.
	\\\bigskip
	\textbf{\textcolor{sapienza}{Future Developments:}} \\
	\begin{itemize}
	\item Test with a larger set of highly evasive malware samples
	\item Improve logging capabilities
	\item Adopt log filtering techniques
	\end{itemize}

### 2018-07-14 conclusions.tex
Slides Done

The obvious next step in BlueTracer's development is to test it with larger a set of highly-evasive malware samples, in order to further evaluate its effectiveness in a real-life scenario.

>>>>

The obvious next step in BlueTracer's development is to test it with larger a set of highly evasive malware samples, in order to further evaluate its effectiveness in a real-life scenario.
